---
title: "ISPE03"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prerequisites

### Equipment and software requirements

Attendees are expected to use their own computers with a working version of R (version 3.6.3 or higher) and RStudio (version 1.2 or higher) installed.

R and RStudio are supported by PC, Linux, and Mac OS and can be downloaded for free by following these links
http://www.r-project.org/ and https://www.rstudio.com/products/rstudio/download/#download.

### R packages

Run the code below in R to install all of the required R packages.

```r
install.packages("remotes")
remotes::install_github("geocompr/geocompkg")
```

### Check if it works

Afterwards, run the code below (you should see the map as a result):

```{r}
library(tmap)
library(spData)
library(spDataLarge)
tm_shape(nz) +
  tm_polygons(lwd = 2) +
  tm_shape(nz_elev) +
  tm_graticules() +
  tm_raster()
```

<!-- install.packages("spDataLarge", repos = "https://nowosad.github.io/drat/", type = "source") -->
Please see https://datacarpentry.org/geospatial-workshop/setup.html for instructions on how to install geospatial library dependencies.

<!-- ### Questionnaire -->

<!-- Please also fill the form at https://forms.gle/sdvLXcqFaqHBGBZF8. -->
